Analytic Occultation Light Curves in Reflected Light

### 2020-04-10 tex/ms.tex
more text

\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
\xxx{Add equations for the rotation and change of basis matrices below.}
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system in some frame $\mathcal{F}_0$. In this frame,
the surface (emitted) intensity field of the body is described by a
vector $\mathbf{y}$ of coefficients in the spherical harmonic
basis $\by$:
%
\begin{align}
    \label{eq:by}
    \by & =
    \begin{pmatrix}
        Y_{0, 0}  &
        Y_{1, -1} & Y_{1, 0}  & Y_{1, 1} &
        Y_{2, -2} & Y_{2, -1} & Y_{2, 0} & Y_{2, 1} & Y_{2, 2} &
        \cdot\cdot\cdot
    \end{pmatrix}^\top
    \quad,
\end{align}
%
where the component at index $n$ is $Y_{l,m}$ with
%
\begin{align}
    \label{eq:l-m}
    l & = \floor*{\sqrt{n}}
    \nonumber               \\
    m & = n - l^2 - l
    \quad.
\end{align}
%
An observer views the body from a large distance in the sky frame
$\mathcal{F}$, in which the $x$-axis points to the right,
the $y$-axis points up, and the $z$-axis points out of the sky
toward the observer. Following \citet{Luger2019}, if
an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
we compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
    \quad,
\end{align}
%
where, from right to left, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$
given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
%
$\mathbf{R}' = \mathbf{R}'(x_o, y_o)$ rotates the body on the plane
of the sky into the integration frame $\mathcal{F}'$, in which the
occultor lies along the $+y'$-axis (Equation~\ref{eq:R'}),
%
$\mathbf{A}$ is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed,
whose component at index $n$ is
%
\begin{align}
    \label{eq:bg}
    \tilde{g}_{n}(x, y) & =
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \text{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \, \text{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \text{otherwise}
        \quad,
    \end{dcases}
\end{align}
%
with
%
\begin{align}
    \label{eq:mu-nu}
    \mu & \equiv l - m
    \nonumber          \\
    \nu & \equiv l + m
\end{align}
%
and
%
\begin{align}
    z(x, y) \equiv \sqrt{1 - x^2 - y^2}
    \quad,
\end{align}
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
\citep[Equation~26 in][]{Luger2019}, with $b_o = \sqrt{x_o^2 + y_o^2}$.

If instead no occultor is present, we compute the total
visible flux $f_0$ from this body as
%
\begin{align}
    \label{eq:rTA1Ry}
    f_0 = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
    \quad,
\end{align}
%
where, as before, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
rotates the body from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$,
%
$\mathbf{R}''$ rotates the body on the plane
of the sky into the integration frame
$\mathcal{F}''$ (Equation~\ref{eq:R''})%
\footnote{%
    In \citet{Luger2019}, $\mathcal{F}'' = \mathcal{F}'$, so
    this rotation is trivial: $\mathbf{R}''$ is just the identity matrix.
},
%
$\mathbf{A_1}$ is the change-of-basis matrix from the spherical harmonic
basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
are computed, whose component at index $n$ is
%
\begin{align}
    \tilde{p}_n(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \text{otherwise}
        \quad,
    \end{dcases}
\end{align}
%
and $\rTe$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bp$
\citep[Equation~19 in][]{Luger2019}.

@@

$+x$-axis (defined \xxx{below}).

@@

We may now re-write Equations~(\ref{eq:sTARRy}) and (\ref{eq:rTA1Ry}) to
account for this illumination transformation. The flux during an occultation
is now given by
%
\begin{align}
    \label{eq:sTA2IA1RRy}
    f & =
    \sT(b, \theta', b_o, r_o)
    \mathbf{A_2}
    \mathbf{I}(b, \theta', r_s)
    \mathbf{A_1}
    \mathbf{R}'(x_o, y_o)
    \mathbf{R}(i, \lambda, \vartheta)
    \mathbf{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:theta'}
    \theta' = \atantwo(x_o, y_o) - \atantwo(x_s, y_s)
\end{align}
%
is the angle of the terminator in the frame $\mathcal{F}'$.
Note that we made use of the fact that
$\mathbf{A} = \mathbf{A_2} \mathbf{A_1}$
(Equation~\ref{eq:A}), where $\mathbf{A_1}$ transforms from
the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
$\mathbf{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.

Similarly, the flux when there is no occultation is now given by
%
\begin{align}
    \label{eq:rTIA1RRy}
    f_0 & =
    \rT(b)
    \mathbf{I}(b, \theta'', r_s)
    \mathbf{A_1}
    \mathbf{R}''(x_s, y_s)
    \mathbf{R}(i, \lambda, \vartheta)
    \mathbf{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:theta''}
    \theta'' = 0
\end{align}
%
is the angle of the terminator in the frame $\mathcal{F}''$, by
construction. The transformation
$\mathbf{R}'' = \mathbf{R}''(x_s, y_s)$ (Equation~\ref{eq:R''}) rotates
the body so the semi-major axis of the terminator is aligned
with the $x''$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
this greatly simplifies the integration step.

@@

In order to evaluate the integral in Equation~(\ref{eq:pT}),
we follow the reparametrization tricks of \S{D.2.3} in \citet{Luger2019}.
The algebra is long and tedious, so we merely present the result
(alongside the usual validation links). The $n^\text{th}$ component
of $\pT$ is
%
\begin{proof}{}
    \label{eq:pTsoln}
    \mathbb{p}_n &=
    \begin{dcases}
        %
        %
        2(2r_o)^{l+2}
        V
        \left(
        \frac{\mu+4}{4},
        \frac{\nu}{2},
        0;
        \viI
        \right)
        %
         & \qquad \frac{\mu}{2} \, \text{even}
        \\[1em]
        %
        %
        \mathbb{p}_2
        %
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        %
        (2r_o)^{l-1} \beta
        \left\{
        V
        \left(
        \frac{l-2}{2},
        0,
        0;
        \viJ
        \right) -
        2
        V
        \left(
        \frac{l-2}{2},
        0,
        1;
        \viJ
        \right)
        \right\}
        %
         & \qquad \mu = 1, \,
        l \, \text{even}
        \\[1em]
        %
        %
        (2r_o)^{l-1} \beta
        \left\{
        V
        \left(
        \frac{l-3}{2},
        1,
        0;
        \viJ
        \right) -
        V
        \left(
        \frac{l-3}{2},
        1,
        1;
        \viJ
        \right)
        \right\}
        %
         & \qquad \mu = 1, \, l \ne 1, \,
        l \, \text{odd}
        \\[1em]
        %
        %
        2(2r_o)^{l-1} \beta\,
        V
        \left(
        \frac{\mu-1}{4},
        \frac{\nu-1}{2},
        0;
        \viJ
        \right)
        %
         & \qquad \frac{\mu-1}{2} \, \text{even}, \, l \ne 1
        \\[1em]
        %
        %
        2(2r_o)^{l+2}
        V
        \left(
        \Big\lfloor\frac{\mu + 4}{4}\Big\rfloor,
        \frac{\nu}{2},
        0;
        \viU
        \right)
        %
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        %
        (2r_o)^{l-1} \beta\,
        V
        \left(
        \frac{\mu-1}{4},
        \frac{\nu-1}{2},
        0;
        \viW
        \right)
         & \qquad \mu, \nu \, \text{odd}
        \quad,
        %
        %
    \end{dcases}
    %
\end{proof}
%
where $\beta = \left(1 - (b_o - r_o)^2\right)^\frac{3}{2}$
and we define the Vieta operator
%
\begin{align}
    V\left(u, v, w; \mathbf{x}\right) \equiv
    \sum_{i=0}^{u + v}
    \mathcal{A}_{u, v, i}
    \mathbf{x}_{u + w + i}
\end{align}
%
as the dot product of a vector $\mathbf{x}$ and
the vector of Vieta's theorem coefficients, where
\citep[c.f. Equation~D34 in][]{Luger2019}
%
\begin{align}
    \label{eq:vieta}
    \mathcal{A}_{u,v,i} & =
    \sum_{j=\text{max}(0,u-i)}^{\text{min}(u+v-i,u)}
    \binom{u}{j}
    \binom{v}{u+v-i-j}
    (-1)^{u+j}\left(\frac{b_o-r_o}{2r_o}\right)^{u+v-i-j}
    \quad.
\end{align}
%
The vectors $\viI$, $\viJ$,
$\viU$, and $\viW$ are solutions
to specific integrals, which we compute recursively below. As in
\citet{Luger2019} the $n = 2$ term of $\pT$ (second case in the
equation above) is handled separately; we also compute this below.

@@

\subsubsection{The vector $\viU$}
\label{sec:U}
%
The components of the vector $\viU$ are given by the integral
%
\begin{align}
    \label{eq:U}
    \iU_v(\vkappa) =
    \vint{\vkappa}{\cos\varphi\sin^{2v}\varphi}
    \quad.
\end{align}
%
This integral has an analytic solution for all $v$:
%
\begin{proof}{U}
    \label{eq:Usol}
    \iU_v(\vkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
    \quad.
\end{proof}

\subsubsection{The vector $\viW$}
\label{sec:W}
%
The components of the vector $\viW$ are given by the integral
%
\begin{align}
    \label{eq:W}
    \iW_v(\vkappa) = ???
    \quad.
\end{align}
%
This integral also has a closed-form solution:
%
\begin{proof}{}
    \label{eq:Wsol}
    \iW_n =
    \frac{\sin^{2n + 2}\left(\frac{\vkappa}{2}\right)}{2n + 5}
    \left(
    \frac{3}{n+1}
        {_2F_1}\left(-\frac{1}{2}, n + 1; n + 2; 1 - q^2\right) + 2 q^3
    \right)
    \quad,
\end{proof}
%
where ${_2F_1}(a, b; c; z)$ is the Gauss hypergeometric function.
%
\xxx{Figure out the integral form, and write up the recursion relations.}

>>>>

\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system in some frame $\mathcal{F}_0$. In this frame,
the surface (emitted) intensity field of the body is described by a
vector $\mathbf{y}$ of coefficients in the spherical harmonic
basis $\by$:
%
\begin{align}
    \label{eq:by}
    \by & =
    \begin{pmatrix}
        Y_{0, 0}  &
        Y_{1, -1} & Y_{1, 0}  & Y_{1, 1} &
        Y_{2, -2} & Y_{2, -1} & Y_{2, 0} & Y_{2, 1} & Y_{2, 2} &
        \cdot\cdot\cdot
    \end{pmatrix}^\top
    \quad,
\end{align}
%
where the component at index $n$ is $Y_{l,m}$ with
%
\begin{align}
    \label{eq:l-m}
    l & = \floor*{\sqrt{n}}
    \nonumber               \\
    m & = n - l^2 - l
    \quad.
\end{align}
%
An observer views the body from a large distance in the sky frame
$\mathcal{F}$, in which the $x$-axis points to the right,
the $y$-axis points up, and the $z$-axis points out of the sky
toward the observer. Following \citet{Luger2019}, if
an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
we compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
    \quad,
\end{align}
%
where, from right to left, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$
given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$
\citep[Appendix C in][]{Luger2019},
%
$\mathbf{R}' = \mathbf{R}'(x_o, y_o)$ rotates the body on the plane
of the sky into the integration frame $\mathcal{F}'$, in which the
occultor lies along the $+y'$-axis,
%
$\mathbf{A}$
\citep[Equation~B13 in][]{Luger2019}
is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed,
whose component at index $n$ is
%
\begin{align}
    \label{eq:bg}
    \tilde{g}_{n}(x, y) & =
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \text{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \, \text{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \text{otherwise}
        \quad,
    \end{dcases}
\end{align}
%
with
%
\begin{align}
    \label{eq:mu-nu}
    \mu & \equiv l - m
    \nonumber          \\
    \nu & \equiv l + m
\end{align}
%
and
%
\begin{align}
    z(x, y) \equiv \sqrt{1 - x^2 - y^2}
    \quad,
\end{align}
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
\citep[Equation~26 in][]{Luger2019}, with $b_o = \sqrt{x_o^2 + y_o^2}$.

If instead no occultor is present, we compute the total
visible flux $f_0$ from this body as
%
\begin{align}
    \label{eq:rTA1Ry}
    f_0 = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
    \quad,
\end{align}
%
where, as before, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
rotates the body from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$,
%
$\mathbf{R}''$ rotates the body on the plane
of the sky into the integration frame
$\mathcal{F}''$%
\footnote{%
    In \citet{Luger2019}, $\mathcal{F}'' = \mathcal{F}'$, so
    this rotation is trivial: $\mathbf{R}''$ is just the identity matrix.
},
%
$\mathbf{A_1}$
\citep[Equation~B11 in][]{Luger2019}
is the change-of-basis matrix from the spherical harmonic
basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
are computed, whose component at index $n$ is
%
\begin{align}
    \label{eq:bp}
    \tilde{p}_n(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \text{otherwise}
        \quad,
    \end{dcases}
\end{align}
%
and $\rTe$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bp$
\citep[Equation~19 in][]{Luger2019}.

@@

$+x$-axis (a frame-dependent quantity, defined below).

@@

We may now re-write Equations~(\ref{eq:sTARRy}) and (\ref{eq:rTA1Ry}) to
account for this illumination transformation. The flux during an occultation
is now given by
%
\begin{align}
    \label{eq:sTA2IA1RRy}
    f & =
    \sT(b, \theta', b_o, r_o)
    \mathbf{A_2}
    \mathbf{I}(b, \theta', r_s)
    \mathbf{A_1}
    \mathbf{R}'(x_o, y_o)
    \mathbf{R}(i, \lambda, \vartheta)
    \mathbf{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:theta'}
    \theta' = \atantwo(x_o, y_o) - \atantwo(x_s, y_s)
\end{align}
%
is the angle of the terminator in the frame $\mathcal{F}'$.
Note that we made use of the fact that
$\mathbf{A} = \mathbf{A_2} \mathbf{A_1}$
\citep[Equation~14 in][]{Luger2019}, where $\mathbf{A_1}$ transforms from
the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
$\mathbf{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.

Similarly, the flux when there is no occultation is now given by
%
\begin{align}
    \label{eq:rTIA1RRy}
    f_0 & =
    \rT(b)
    \mathbf{I}(b, \theta'', r_s)
    \mathbf{A_1}
    \mathbf{R}''(x_s, y_s)
    \mathbf{R}(i, \lambda, \vartheta)
    \mathbf{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:theta''}
    \theta'' = 0
\end{align}
%
is the angle of the terminator in the frame $\mathcal{F}''$, by
construction. The transformation
$\mathbf{R}'' = \mathbf{R}''(x_s, y_s)$ rotates
the body
through an angle $\atantwo(x_s, y_s)$
so the semi-major axis of the terminator is aligned
with the $x''$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
this greatly simplifies the integration step.

@@

In order to evaluate the integral in Equation~(\ref{eq:pT}),
we follow the reparametrization tricks of \S{D.2.3} in \citet{Luger2019}.
The algebra is long and tedious, so we merely present the result
(alongside the usual validation links). The $n^\text{th}$ component
of $\pT$ is
    \label{eq:pTsoln}
    \mathbb{p}_n & =
    \resizebox{.8\hsize}{!}{$
                2(2r_o)^{l+2}
                    V
                    \frac{\mu+4}{4},
                    \frac{\nu}{2},
                    0;
                    \viI
                     & \qquad \qquad \qquad \qquad \qquad
                    \qquad \qquad \qquad \quad
                    \frac{\mu}{2} \, \text{even}
                    V
                    \frac{\mu + 2}{2},
                    \frac{\nu}{2},
                    0;
                    \viU
                     & \qquad \qquad \qquad \qquad \qquad
                    \qquad \qquad \qquad \quad
                    \frac{\mu}{2} \, \text{odd}
                 & \qquad
                \mu, \nu \, \text{even}
                \\[2em]
                \mathbb{p}_2
                 & \qquad
                \mu = \nu = 1
                \\[1.5em]
                \beta (2r_o)^{l-1}
                        V
                        \frac{l-2}{2},
                        0,
                        0;
                        \viJ
                        \right) -
                        2
                        V
                        \frac{l-2}{2},
                        0,
                        1;
                        \viJ
                         & \qquad \quad
                        l \, \text{even}
                        V
                        \frac{l-3}{2},
                        1,
                        0;
                        \viJ
                        \right) -
                        2V
                        \frac{l-3}{2},
                        1,
                        1;
                        \viJ
                         & \qquad \quad
                        l \, \text{odd} \ne 1
                     & \qquad
                    \mu = 1
                    \\[3em]
                        2
                        V
                        \frac{\mu-1}{4},
                        \frac{\nu-1}{2},
                        0;
                        \viJ
                         & \qquad \qquad \qquad \qquad
                        \frac{\mu - 1}{2} \, \text{even}
                        2
                        V
                        \frac{\mu-1}{4},
                        \frac{\nu-1}{2},
                        0;
                        \viW
                         & \qquad \qquad \qquad \qquad
                        \frac{\mu - 1}{2} \, \text{odd}
                     & \qquad
                    \mu > 1
                 & \qquad
                \mu, \nu \, \text{odd}
        $}
where $\beta = \left(1 - (b_o - r_o)^2\right)^\frac{3}{2}$
and we define the Vieta operator
    V\left(u, v, w; \mathbf{x}\right) \equiv
    \sum_{i=0}^{u + v}
    \mathcal{A}_{u, v, i}
    \mathbf{x}_{u + w + i}
as the dot product of a vector $\mathbf{x}$ and
the vector of Vieta's theorem coefficients, where
\citep[c.f. Equation~D34 in][]{Luger2019}
    \label{eq:vieta}
    \mathcal{A}_{u,v,i} & =
    \sum_{j=\text{max}(0,u-i)}^{\text{min}(u+v-i,u)}
    \binom{u}{j}
    \binom{v}{u+v-i-j}
    (-1)^{u+j}\left(\frac{b_o-r_o}{2r_o}\right)^{u+v-i-j}
The vectors $\viI$, $\viJ$,
$\viU$, and $\viW$ are solutions
to specific integrals, which we compute recursively below. As in
\citet{Luger2019} the $n = 2$ term of $\pT$, $\mathbb{p}_2$,
is handled separately; we also compute this below.

Note that several of the cases in Equation~(\ref{eq:pTsoln}) are
identical to those in Equation~(D35) of \citet{Luger2019}, provided
we replace their integrals $\mathcal{I}$ and $\mathcal{J}$ with our
integrals $\viI$ and $\viJ$, respectively. The integrals themselves
are similar, except for a change in the limits of integration, which
are no longer symmetric about zero. As we will see, this leads to the
dependence of these expressions on \emph{incomplete} elliptic integrals.
Note also that the integrals $\viU$ and $\viW$ are new, as certain
cancellations in \citet{Luger2019} resulted in the corresponding cases
contributing zero net flux \citep[last case in Equation~D35 of][]{Luger2019}.

@@

\subsubsection{The vector $\viU$}
\label{sec:U}
%
The components of the vector $\viU$ are given by the integral
%
\begin{align}
    \label{eq:U}
    \iU_v(\vkappa) =
    \vint{\vkappa}{\cos\varphi\sin^{2v}\varphi}
    \quad.
\end{align}
%
This integral has an analytic solution for all $v$:
%
\begin{proof}{U}
    \label{eq:Usol}
    \iU_v(\vkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
    \quad.
\end{proof}
%

\subsubsection{The vector $\viW$}
\label{sec:W}
%
The components of the vector $\viW$ are given by the integral
%
\begin{align}
    \label{eq:W}
    \iW_v(k^2, \vkappa) =
    \vint{\vkappa}{
        \cos\varphi\sin^{2v + 1}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad.
\end{align}
%
We may compute it by either upward or downward recursion. In the upward
case, we start with the lower boundary condition
%
\begin{proof}{}
    \iW_0 &= \Delta
    \Bigg\{
    \frac{\sinhalfkap[2]}{5}
    \left(
    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{1 - \mathbf{q}(k^2, \vkappa)^3}
    +
    \mathbf{q}(k^2, \vkappa)^3
    \right)
    \Bigg\}
    \quad.
\end{proof}
%
Defining
%
\begin{align}
    \mathbf{c}_0(k^2, \vkappa) & =
    \sinhalfkap[4]
    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \quad,
\end{align}
%
we may recurse upward in $\iW$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{}
    \label{eq:Wv}
    \iW_v                      & =
    \frac{\Delta}{2v + 5}
    \left(
    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \iW_{v - 1}
    - \mathbf{c}_{v - 1}(k^2, \vkappa)
    \right)
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
\end{proof}
%
for $v > 0$.
%
In the case of downward recursion, we start with the upper boundary
condition for $v = \vmax$,
%
\begin{proof}{}
    \label{eq:Wsol}
    \iW_\vmax &=
    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{\vmax + \frac{5}{2}}
    \left(
    \mathbf{f}_\vmax(k^2, \vkappa)
    + 2 \mathbf{q}(k^2, \vkappa)^3
    \right)
    \quad,
\end{proof}
%
where
%
\begin{proof}{}
    \mathbf{f}_v(k^2, \vkappa)
    &\equiv
    \frac{3}{v+1}
    \,
    {_2\mathbf{F}_1}\left(
    -\frac{1}{2},
    v + 1;
    v + 2;
    1 - \mathbf{q}(k^2, \vkappa)^2
    \right)
\end{proof}
%
and ${_2\mathbf{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
hypergeometric function.
We then recurse downward \xxx{...}
\xxx{TODO: Check these expressions.}
